There once was a grid at ol' Carkeek

### 2016-08-13 Manuscript/v0.0/carkeek_grid.tex
add some basic sequencing results

We checked for experimental error by evaluating the Bray-Curtis dissimilarity of proportional read abundance among replicate PCRs of the same DNA sample (0.033$\pm$0.063), and excluded one PCR replicate for which the dissimilarities between itself and the other replicates exceeded 1 SD (lib\_B\_tag\_GCGCTC).

%RESULTS
%Reads were of generally high-quality, with XXX% of base calls having a 0.001 or lower probability of incorrect base call (Phred q-score of 30 or higher).
%Total sequencing clusters passing filter per read: 371,576,190 on NEXTSEQ
%
% THESE BELOW ARE FROM A MISEQ RUN
% reads passing filter, % >= Q30, for each run ( 7,052,307 ; 6,752,829; 97.47 :: 7,052,307 ; 6,752,829 ; 95.50)
%
%Cluster density of 358 \UTF{00EF}\UTF{00BF}\UTF{0153}22	clusters per mm^2
%
%XXX % of reads aligned to the PhiX genome
%(31.02 \UTF{00EF}\UTF{00BF}\UTF{0153}0.59	; 29.17 \UTF{00EF}\UTF{00BF}\UTF{0153}0.89)
%
%and error rate as determined from alignment of PhiX reads to the PhiX genome was low (Read 1: 1.26 \UTF{00EF}\UTF{00BF}\UTF{0153}0.07; Read 2: 1.38 \UTF{00EF}\UTF{00BF}\UTF{0153}0.07)
%----------------------------------------------------------------------------

@@

\subsection*{Data Quality (Bioinformatics)}
Raw sequence data in fastq format is publicly available (see Data Availability).
All value ranges are reported as (mean $\pm$ standard deviation).\\
There was a very low frequency of cross-contamination from other libraries into those reported here (5e-05$\pm$8e-05; max 0.00034)

>>>>

We checked for experimental error by evaluating the Bray-Curtis dissimilarity of proportional read abundance among replicate PCRs from the same DNA sample (0.033$\pm$0.063), and excluded one PCR replicate for which the dissimilarities between itself and the other replicates exceeded 1 SD.% (lib\_B\_tag\_GCGCTC)

@@

\subsection*{Data Quality (Bioinformatics)}
Raw sequence data in fastq format is publicly available (see Data Availability).
All value ranges are reported as (mean $\pm$ standard deviation).
A total of 371,576,190 reads passing filter were generated in each direction, with XXX\% of base calls having a 0.001 or lower probability of incorrect base call (Phred q-score of 30 or higher).
%XXX % of reads aligned to the PhiX genome
%and error rate as determined from alignment of PhiX reads to the PhiX genome was low (Read 1: 1.26 \UTF{00EF}\UTF{00BF}\UTF{0153}0.07; Read 2: 1.38 \UTF{00EF}\UTF{00BF}\UTF{0153}0.07)
There was a very low frequency of cross-contamination from other libraries into those reported here (5e-05$\pm$8e-05; max 0.00034)
